\section{Conclusion}
This paper presents a reproducible experimental pipeline for forecasting Indonesian bank stock prices using recurrent sequence models, macroeconomic features, multi-seed evaluation, feature-attribution outputs, and paired statistical testing.

Within the original recurrent benchmark, BiLSTM-based settings generally outperform LSTM across the evaluated banks, with best-case RMSE gains over the \texttt{lstm\_data} baseline reaching up to 35.66\%. Diebold-Mariano tests indicate significant forecast-error reduction in six banks, while Wilcoxon results are less conclusive due to the five-seed sample. Macro features and budgeted tuning are not uniformly beneficial, so the evidence favors bank-specific model selection rather than one fixed configuration for all emitents.

The supplementary architecture experiments change the follow-up direction rather than the validation status of the original benchmark. Informer/Autoformer runs produce the lowest observed aggregate errors among the completed families, with \texttt{informer\_data} reaching RMSE 401.02, MAE 325.11, and MAPE 5.94\%. Recurrent variants based on normalization, convolution, and attention broaden the ablation space, but they do not improve the original recurrent baseline on average. Thus, Transformers are the strongest candidate for paired cross-family validation, while recurrent variants are better interpreted as architecture-ablation evidence.

Several limitations should be noted. First, the evaluation is restricted to seven Indonesian banking stocks, which constrains generalizability to other markets and sectors. Second, the five-seed protocol limits statistical power for nonparametric tests. Third, Transformer and recurrent-variant statistical tests should be regenerated from raw prediction outputs to match the original recurrent validation depth. Fourth, recurrent variants currently lack SHAP outputs because the 1400-run sweep was executed without SHAP for compute-cost control.

Immediate future work includes: (i) extending validation to walk-forward protocols, (ii) increasing seed count for stronger nonparametric testing power, (iii) ablation on feature lag to investigate whether temporal misalignment explains macro feature failures, and (iv) paired statistical validation and targeted SHAP analysis across the best recurrent, Transformer, and recurrent-variant cases.
