\section{Experimental Setup}

\subsection{Evaluation Metrics}
Primary metrics are MSE, RMSE, MAE, and MAPE on the test partition. We report both point estimates (mean) and seed-wise variability (standard deviation) across five independent runs to characterize stability.

\subsection{Primary Recurrent Benchmark}
The main ablation factors are:
\begin{itemize}
    \item \textbf{Model family}: LSTM and BiLSTM
    \item \textbf{Feature regime}: \texttt{Without\_Macro} (10 features) vs \texttt{With\_Macro} (16 features)
    \item \textbf{Optimization mode}: default ($h{=}64, \alpha{=}10^{-3}, L{=}20$) vs GA-optimized (``\_ga'')
\end{itemize}
This yields $2 \times 2 \times 2 = 8$ recurrent-model cases per bank for controlled comparison, or 280 recurrent runs across seven banks and five seeds.

\subsection{Supplementary Extension Experiments}
Additional experiments evaluate two architecture-extension groups using the same bank and seed protocol. The Transformer extension contains Informer and Autoformer cases under price-only and macro regimes, including fast random-search variants, for 280 runs. The recurrent-variant extension contains normalization, convolutional recurrent, and attention-augmented LSTM/BiLSTM variants, for 1400 runs. These runs are reported as supplementary evidence because paired statistical tests across all model families have not yet been regenerated.

\subsection{Multi-Seed Protocol}
Each configuration is executed with five seeds: $\{42, 52, 62, 72, 82\}$. The complete run table stores configuration metadata, per-epoch metrics, and file paths for downstream significance analysis. All cases use identical data splits and seed sets to ensure fairness.

\subsection{Implementation Details}
Implementation is based on Python and PyTorch. Training uses the Adam optimizer with ReduceLROnPlateau scheduling and validation-based early stopping. The recurrent baseline uses batch size 32 in the original study; GPU-accelerated Transformer and recurrent-variant sweeps use larger batch configurations where supported by memory. The forecasting horizon is one day. Code and outputs are organized under the project repository, with raw experiment artifacts stored in \texttt{code/results\_study\_full}, \texttt{code/results\_transformer\_study}, and \texttt{code/results\_recurrent\_variants\_study}.

\subsection{Cross-Model Fairness Protocol}
To maintain fairness, all reported families use identical bank sets, chronological splits, and seed sets. Feature regimes are matched as price-only or macro-augmented. Optimization budgets are kept budgeted rather than exhaustive, so results should be interpreted as controlled experimental evidence rather than a claim of globally optimal hyperparameters.
